\documentclass{article}

\usepackage{ulem}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{booktabs}

\title{SE 3XA3: Problem Statement\\TankWar}

\author{Team \#212, Genius
		\\Di Wu, 400117248, wud43 
		\\Jiahao Zhou, 400082351, zhouj56 
		\\Xinyu Huang, 400120376, huangx65
}

\date{}



\begin{document}

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
22 January 2020 & Xinyu Huang, Di Wu, Jiahao Zhou & Create the first version of the Problem Statement\\
\textcolor{red}{02 April 2020} & \textcolor{red}{Xinyu Huang, Di Wu, Jiahao Zhou} & \textcolor{red}{Add some clients, and details about the hardware requirment}\\
\bottomrule
\end{tabularx}
\end{table}

\newpage

\maketitle

\section{What problem are you trying to solve?}
\newcommand*\apos{\textsc{\char13}}
Many people born in 20 century have experience with the classic Family Computer games in their childhood. Those games brought pure pleasure to the children at that generation and became a precious memory to them. Nowadays people start to get bored with normal video games, and many of them miss the pure happiness gained from the video games that they played in childhood. However, the Family Computer platform is no longer produced and the games are not updated for decades. As game developers, we are trying to recreate and upgrade the Family Computer games on the modern computer platform to let people have an easy access to those games and feel the same pleasure in their childhood again.

\section{Why is this an important problem?}

The original game Battle City published in 1985 was a very classic game on the Family Computer platform. It was one of the most popular games in the Family Computer game history. At the end of 20th century, most of the children, especially the boys had a lot of fun by playing it, and it became a precious memory in their childhood.  Many people at that generation are very desired to recreate the happy moment by playing the game again. However, the Family Computer is no longer manufactured and the game Battle City is also not updated for more than 20 years. It is hard for people to find a Family Computer to play Battle City. Therefore, our group is going to recreate and provide updated version of the Battle City game as a new game called TankWar on modern computers to allow people have easy access for free. People who used to enjoy it can recall their childhood, and also the children who may never hear about this game can enjoy the game. We believe that this new game can attract a large amount of people and allow them to have much fun. 

\section{What is the context of the problem you are solving?}

The stakeholders of this software includes game players \textcolor{red}{which are those people above 12 years and may like the game. There are also clients include the professor and the TAs of this course, } and software developers \textcolor{red}{who are the team members}. TankWar will be the best choice for people to improve their mood and relax during the free time. Software developers not only need to develop the initial version of the software, but also need to update and maintain the software in the future. \\
\\
TankWar is developed based on python, therefore it can be run in Windows \textcolor{red}{7 and later}, OS X, and Linux environments with the installation of pygame. Besides, the TankWar is a 2-D small game, so it \textcolor{red}{\sout{does not have a high requirement}} \sout{\textcolor{red}{for hardware}} \textcolor{red}{only needs a personal compter with 2-cores processor and 1GB RAM}. Basically, every computer can run the game.



\end{document}